---
title: 'Tidy Tuesday #1'
author: "Xinyi Li"
output: 
  html_document:
    df_print: paged
    code_download: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)     # for graphing and data cleaning
library(lubridate)     # for date manipulation
library(ggthemes)      # for even more plotting themes
library(fmsb)          # for the radar chart
theme_set(theme_minimal()) # My favorite ggplot() theme :)
```

## Data choice 1: Dog breed data

```{r}
breed_traits <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-02-01/breed_traits.csv')
trait_description <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-02-01/trait_description.csv')
breed_rank_all <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-02-01/breed_rank.csv')
data(breed_traits)
```


**Question:Strangers Openness Level Count of 195 Dog Breeds: How many breeds are there in each level? **

```{r}
breed_traits %>% 
  ggplot(aes(x=`Openness To Strangers`))+
  geom_bar(aes(y=..count..),fill='lightblue',color='steelblue')+
  stat_bin(aes(y=..count.., label=ifelse(..count..==0,"",..count..)),geom="text", vjust=-.5)+
  theme(panel.grid.major = element_blank())+
  labs(title='Strangers Openness Level of 195 Dog Breeds',y='Numbers of Breeds for each level',x='Strangers Openness Level')+
  theme(plot.title = element_text(hjust = 0.5,colour = "black", face = "bold", 
    size = 18, vjust = 1))+
  scale_x_continuous(breaks=0:5)+
  theme()

```






**Extra: for advice instead of submission: 10 traits of a breed**

```{r}
#This chunk is for the extra radar chart: just want to get some advice
total<-cbind(breed_rank_all,breed_traits)
special<-total[2,]
new<-special %>% 
  select(`Affectionate With Family`:`Mental Stimulation Needs`)
new<-new[,c(-7,-8,-11,-12,-13,-14)]
new<-as.integer(new)

# Create data: 
data <- as.data.frame(matrix( new , ncol=10))

colnames(data) <- c("Family Affectionate" , "Children Goodness" , "Dogs Goodness" , "Shedding Level" , "Coat Grooming\n Frequency", "  Drooling Level" , "     Strangers\n Openness" , "Playfulness Level", "Protective Nature", "Adaptability Level" )
 
data <- rbind(rep(20,10) , rep(0,10) , data)
 
#par(mfrow=c(1,3)) #this is for more charts 
radarchart(data,title = "French Bulldog Profile")


```



This week's data is about Dog Breeds. Read more about it, including definitions of variables, [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-02-01/readme.md). 

## Data choice 2: Board games

```{r}
ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/ratings.csv')
details <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/details.csv')
```

Read more about the board game data, including definitions of variables, [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-01-25/readme.md). 

## Instructions and tips

For this first week, keep your plot simple but meaningful. Don't try to do something really hard, especially right now when you're still developing your R coding skills. Take a minute to plan out on paper or the white board what you want your plot to look like and then dive into the code. And make sure to read about what the variables are first! 

When you are finished, please delete all the unneeded code and instructions and uncomment (delete the `#`) in the options section of code at the top. If you feel up for it, we encourage you to tweet out your graph with the `#TidyTuesday` hashtag and tag `@lisalendway` (Prof. Lisa) and `@Sintripetal` (Prof. Lauren). See the Tidy Tuesday description file if you want to use our `@MacTidyTuesday` Twitter account to do that. PLEASE take a moment to read the message at the top about alt text. If you want to post on Twitter, be sure to add that. If you need help, ask. Also, consider adding a caption or tag label with your name and source of the dataset. You can do this by adding something like: `labs(caption = "Plot created by YOURNAME, data from DATASOURCE")` to your plot code.

