---
title: 'Tidy Tuesday #3'
author: "Xinyi Li"
output: 
  html_document:
    df_print: paged
    code_download: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)     # for graphing and data cleaning
library(lubridate)     # for date manipulation
library(ggthemes)      # for even more plotting themes
theme_set(theme_minimal()) # My favorite ggplot() theme :)

library(tidyverse)     # for data cleaning and plotting
library(lubridate)     # for date manipulation
library(openintro)     # for the abbr2state() function
library(palmerpenguins)# for Palmer penguin data
library(maps)          # for map data
library(ggmap)         # for mapping points on maps
library(gplots)        # for col2hex() function
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(carData)       # for Minneapolis police stops data
library(ggthemes)      # for more themes (including theme_map())
library(googlesheets4) # for reading googlesheet data

```

## Data choice 1: Freedom Data

```{r}
# Read in the data

freedom <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-02-22/freedom.csv')

# If the code above gives an error, uncomment the code below and use it instead. 
# You will need to install the tidytuesdayR package first.

# library(tidytuesdayR)
# 
# tuesdata <- tidytuesdayR::tt_load('2022-02-22')
# tuesdata <- tidytuesdayR::tt_load(2022, week = 8)
# 
# freedom <- tuesdata$freedom
```

This week's data is about civil freedoms around the world. Read more about it, including definitions of variables, [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-02-22/readme.md). 

## Data choice 2: Alternative fuel stations

```{r}

# Read in the data

stations <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-03-01/stations.csv')

# If the code above gives an error, uncomment the code below and use it instead. 
# You will need to install the tidytuesdayR package first.

# library(tidytuesdayR)
# 
# tuesdata <- tidytuesdayR::tt_load('2022-03-01')
# tuesdata <- tidytuesdayR::tt_load(2022, week = 9)
# 
# stations <- tuesdata$stations

stations %>% 
  group_by(FACILITY_TYPE) %>% 
  summarise(n=n()) %>% 
  arrange(desc(n))
```

Read more about the Alternative fuel stations data, including definitions of variables, [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-03-01/readme.md). 

**Try to visualize:Alternative fuel stations' special facility(choose 5 facility type) distribution**
```{r,fig.alt="Fuel station position",fig.width=8}
us<-map_data("state")
stations<-stations %>% 
  filter(X>=-140,X<=-50,Y<=65,
         FACILITY_TYPE%in%c("FUEL_RESELLER","CONVENIENCE_STORE","CAR_DEALER","MUNI_GOV","FED_GOV","RENTAL_CAR_RETURN","CAR_DEALER","HOTEL")) %>% 
  mutate(state_name = str_to_lower(abbr2state(`STATE`))) %>% 
  group_by(state_name) %>% 
  mutate(stations=n())
  
stations %>% 
  ggplot() +
  geom_map(map = us ,
           aes(map_id = state_name, 
               fill = stations)) + 
  expand_limits(x = us$long , y =us$lat) + 
  geom_point(data = stations %>% filter(COUNTRY == "US", !(`state_name` %in% c("hawaii","alaska"))) ,
             aes(x = X, y = Y,
             color = FACILITY_TYPE),
             size = .05,
             alpha = .2) +
  guides(colour = guide_legend(override.aes = list(size=8)))+
  labs(title="Alternative fuel stations' special facility distribution among US",
       color = "Facility Type",
       fill="stations total number",
       caption = "Chose 5 facility types with most stations for viewing.
       Created by Xinyi, Data from US DOT.")+
  theme(legend.background = element_blank(),
        plot.background = element_rect(fill = "#ede2d1", color = "#8c7b5f"),
        plot.title = element_text(face="bold",size=14,hjust=0.5),
        panel.grid = element_blank(),
        axis.title.x=element_blank(),
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank())+
  theme(plot.caption.position = "plot",
        plot.caption = element_text(hjust = 1,colour = "darkgray"))

#next time: try geom_bar+coord_polar and grid arrange
#change legend.key
#enlarge points on plot?
```








## Instructions and tips

ake a minute to plan out on paper or the white board what you want your plot to look like and then dive into the code. And make sure to read about what the variables are first! 

When you are finished, please delete all the unneeded code and instructions and uncomment (delete the `#`) in the options section of code at the top. If you feel up for it, we encourage you to tweet out your graph with the `#TidyTuesday` hashtag and tag `@lisalendway` (Prof. Lisa) and `@Sintripetal` (Prof. Lauren). See the Tidy Tuesday description file if you want to use our `@MacTidyTuesday` Twitter account to do that. PLEASE take a moment to read the message at the top about alt text. If you want to post on Twitter, be sure to add that. If you need help, ask. Also, consider adding a caption or tag label with your name and source of the dataset. You can do this by adding something like: `labs(caption = "Plot created by YOURNAME, data from DATASOURCE")` to your plot code.

